Object naming on steroids

### 2019-05-06 papers/ACL2019/intro.tex
all recent changes

The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories. And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy. For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.

@@

The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names. We show that this simple, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl19_naming"
%%% End:

>>>>

The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories. And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy. For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc. Hence, when speaker name objects, e.g.\ when referring to it, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.

@@

The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of,

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
